Towards a Pandemic-Scale Ancestral Recombination Graph of SARS-CoV-2

### 2023-05-05 paper.tex
Yans updates

    Nodes & & 1,453,347 & & 783,231  & \\
    & Samples & 1,265,685 & (87.09\%) & 657,239 & (83.91\%) \\
    & Local (UPGMA) & 102,709 & (7.07\%) & 51,807 & (6.61\%)  \\
    & Reversion push & 40,538 & (2.79\%) & 34,358 & (4.39\%)  \\
    & Mutation collapse & 40,292 & (2.77\%) & 37,749 & (4.82\%)  \\
    & Recombination & 4,123 & (0.28\%) & 2,078 & (0.27\%) \\
    \cmidrule{2-6}
    % TODO add more information on mutations
    Mutations & & 1.21M &  & 1.06M & \\
    & On one sample & 759K & (63\%) & 767K & (72\%) \\
    & Reversions & 72K & (5.98\%) & 48K & (4.54\%) \\
    & per node & 0.83  &   & 1.36 \\
    \cmidrule{2-6}
    Recombination events & \\
    & Total & 4,123 & & 2,078 & \\
    & Singletons & 2,601  & (63\%) & 1,315 & (63\%) \\
    % clearer for many than "local trees?"
    & Unique breakpoints & 1,496 &  & 958 & \\
    \cmidrule{2-6}
    \multicolumn{2}{l}{Size (inc metadata)} & 57MB & & 36MB&  \\
    \multicolumn{2}{l}{Bytes/sample (exc metadata)}  & 8.29  & & 10.83 \\
    Load time & & 0.9s & & 0.5s & \\
    \bottomrule
\end{tabular}
\end{center}

>>>>

    Nodes & & 1,453,347 & & 783,231  & \\
    & Samples & 1,265,685 & (87\%) & 657,239 & (84\%) \\
    & Local (UPGMA) & 103K & (7.1\%) & 52K & (6.6\%)  \\
    & Tree adjustment & 80,830 & (5.6\%) & 72,107 & (9.2\%) \\
    & Recombination & 4,123 & (0.33\%) & 2,078 & (0.27\%) \\
    \cmidrule{2-6}
    % TODO add more information on mutations
    Mutations & & 1.21M &  & 1.06M & \\
    & On one sample & 759K & (63\%) & 767K & (72\%) \\
    & Reversions & 72K & (5.98\%) & 48K & (4.54\%) \\
    & per node & 0.83  &   & 1.36 \\
    \cmidrule{2-6}
    Recombination events & \\
    & Total & 4,123 & & 2,078 & \\
    & Singletons & 2,601  & (63\%) & 1,315 & (63\%) \\
    % clearer for many than "local trees?"
    & Unique breakpoints & 1,496 &  & 958 & \\
    \cmidrule{2-6}
    \multicolumn{2}{l}{Size (inc metadata)} & 57MB & & 36MB&  \\
    \multicolumn{2}{l}{Bytes/sample (exc metadata)}  & 8.29  & & 10.83 \\
    Load time & & 0.9s & & 0.5s & \\
    \bottomrule
\end{tabular}
\end{center}
